How not to constructivize cohomology

### 2018-10-15 slides-pssl104.tex
Notes for every slide finished, now fine-tuning

  \jnote{1-}{Even if we could constructively prove that there are enough flabby
  modules, there is still the problem that the proof that flabby
  sheaves of modules are acyclic for the global sections functor (appears to)
  require Zorn's lemma.}
\end{frame}
\addtocounter{framenumber}{-1}

>>>>

  \jnote{1-}{Even if we could constructively prove that there are enough flabby
  modules, there is still the problem that the proof that flabby
  sheaves of modules are acyclic for the global sections functor (appears to)
  require Zorn's lemma.

  Hence it appears that the simple idea of basing sheaf cohomology on flabby
  resolutions doesn't work, constructively. More work is needed to give a
  constructive account of sheaf cohomology and, more generally, derived functors.

  I hope that some day, we can study the cohomology of the the smallest dense
  sublocale of the one-point space.$^\star$

  \bigskip
  \bigskip
  \bigskip
  \bigskip

  $^\star$ Assuming the law of excluded middle, this locale is just
  the one-point space again. Hence cohomology of this locale should measure the
  extent to which we're nonclassical, being zero if and only if the law of
  excluded middle holds.

  An alternative way to phrase this question is as follows.
  Let~$\Set_{\neg\neg}$ be the smallest dense subtopos of~$\Set$, the topos of
  double-negation sheaves. The forgetful functor~$\mathrm{Ab}(\Set_{\neg\neg})
  \to \mathrm{Ab}$ is left-exact, but might not be right-exact, since
  a map~$f : A \to B$ is an epimorphism
  in~$\mathrm{Ab}(\Set_{\neg\neg})$ if and only if~$\forall y \in B\_
  \neg\neg(\exists x \in A\_ f(x) = y)$, which is weaker than being surjective.
  What do its right derived functors look like?\par}
\end{frame}
\addtocounter{framenumber}{-1}
